---
title: "动态报告语法格式"
execute:
  warning: false
  error: false
  message: false

toc: true
toc-depth: 5
number-sections: true
number-depth: 4

code-fold: show
code-link: true
code-tools: true

knitr:
  opts_chunk: 
    comment: "#>" 
    collapse: TRUE
crossref: 
  fig-title: 图
  fig-prefix: 图
  tbl-title: 表
  tbl-prefix: 表
  eq-title: 式
  eq-prefix: 式
  def-title: 定义
  def-prefix: 定义
  lem-title: 引理
  lem-prefix: 引理
  sec-prefix: 章节

format:
  html:
    theme: cosmo
editor: visual
---

## 基础

+---------------------------------------------------------+-----------------------------------------------------------+
| output                                                  | syntax                                                    |
+---------------------------------------------------------+-----------------------------------------------------------+
| `code`                                                  | \` code \`                                                |
+---------------------------------------------------------+-----------------------------------------------------------+
| **粗体**                                                | `**粗体**`                                                |
+---------------------------------------------------------+-----------------------------------------------------------+
| *斜体*                                                  | `*斜体*`                                                  |
+---------------------------------------------------------+-----------------------------------------------------------+
| [下横线]{.underline}                                    | `[下横线]{.underline}`                                    |
+---------------------------------------------------------+-----------------------------------------------------------+
| ~~删除线~~                                              | `~~删除线~~`                                              |
+---------------------------------------------------------+-----------------------------------------------------------+
| 上标X^2^                                                | `X^2^`                                                    |
+---------------------------------------------------------+-----------------------------------------------------------+
| 下标 X~1~                                               | `X~1~`                                                    |
+---------------------------------------------------------+-----------------------------------------------------------+
| [SAMALL small caps]{.smallcaps}                         | 与小写字母同等高度的大写字母 `[small caps]{.smallcaps}`   |
+---------------------------------------------------------+-----------------------------------------------------------+
| <https://r4ds.hadley.nz/>                               | `<https://r4ds.hadley.nz/>`                               |
+---------------------------------------------------------+-----------------------------------------------------------+
| [quarto](https://quarto.org)                            | `[quarto](https://quarto.org)`                            |
+---------------------------------------------------------+-----------------------------------------------------------+
| {{< video https://www.youtube.com/embed/wo9vZccmqwc >}} | `{{< video https://www.youtube.com/embed/wo9vZccmqwc >}}` |
+---------------------------------------------------------+-----------------------------------------------------------+
| > Blockquote                                            | `> Blockquote`                                            |
+---------------------------------------------------------+-----------------------------------------------------------+

任务列表

-   [ ] x
    -   [x] y
-   [x] z
    -   [ ] q
        -   [ ] w

### 图

```{r}
#| label: fig-plot
#| fig-cap: "plot 点-线"
#| fig-subcap:
#|   - "点"
#|   - "线"
#| layout-ncol: 2
#| column: page-right

plot(1:25,1:25,pch=c(1:25))
plot(1:25,c(1:25)^2,type="b",pch=c(1:25))
```

如左图 @fig-plot-1 所示，点有25种不同的形状，

右图 @fig-plot-2 所示。

#### 流程图

```{mermaid}
sequenceDiagram
  participant Alice
  participant Bob
  Alice->>John: Hello John, how are you?
  loop Healthcheck
    John->>John: Fight against hypochondria
  end
  Note right of John: Rational thoughts <br/>prevail!
  John-->>Alice: Great!
  John->>Bob: How about you?
  Bob-->>John: Jolly good!
```

```{dot}
//| label: fig-simple
//| fig-cap: "This is a simple graphviz graph."
graph G {
  layout=neato
  run -- intr;
  intr -- runbl;
  runbl -- run;
  run -- kernel;
  kernel -- zombie;
  kernel -- sleep;
  kernel -- runmem;
  sleep -- swap;
  swap -- runswap;
  runswap -- new;
  runswap -- runmem;
  new -- runmem;
  sleep -- runmem;
}
```

##### EDA {#sec-eda}

引用章节： @sec-eda and @sec-formula

引用图片 @fig-histogram shows two histograms displaying the distributions of `price` and `area` individually.

```{r}
#| label: fig-histogram
#| code-summary: "直方图"
#| fig-cap: "Histograms of mpg"
#| fig-subcap:
#|   - "Histogram of `cty`s"
#|   - "Histogram of `hwy`s" 
#| fig-alt: "What's this."
#| layout-ncol: 2
#| column: page-right

ggplot(mpg, aes(cty)) +
  geom_histogram() +
  labs(title = "Histogram of cty")

ggplot(mpg, aes(x =hwy)) +
  geom_histogram() +
  labs(title = "Histogram of hwy")
```

## 表格

@tbl-stats displays basic summary statistics for these two variables.

```{r}
#| label: tbl-stats
#| tbl-cap: "Table Summary statistics "

mpg %>%
  summarise(
    mean_displ=mean(displ),
    mean_hwy=mean(hwy),
    mean_cty=mean(cty),
    .by = cyl
    ) %>%
  knitr::kable(digits = c(0, 0, 0, 0, 2))
```

## 公式 {#sec-formula}

Black-Scholes (@eq-black-scholes) is a mathematical model that seeks to explain the behavior of financial derivatives, most commonly options:

$$ \frac{\partial \mathrm C}{ \partial \mathrm t } + \frac{1}{2}\sigma^{2} \mathrm S^{2} \frac{\partial^{2} \mathrm C}{\partial \mathrm C^2}   + \mathrm r \mathrm S \frac{\partial \mathrm C}{\partial \mathrm S}\ =   \mathrm r \mathrm C  $$ {#eq-black-scholes}

We can fit a simple linear regression model of the form shown in @eq-slr.

$$
price = \hat{\beta}_0 + \hat{\beta}_1 \times area + \epsilon
$$ {#eq-slr}

## callouts

-   `note`

-   `warning`

-   `important`

-   `tip`

-   `caution`

::: callout-note
This is a pretty incomplete analysis, but hopefully the document provides a good overview of some of the authoring features of Quarto!
:::

::: {#tip-example .callout-tip}
### 交叉引用 a Tip

Add an ID starting with `#tip-` to reference a tip.
:::

See @tip-example...

| 标注类型    | 前缀    |
|-------------|---------|
| `note`      | `#nte-` |
| `tip`       | `#tip-` |
| `warning`   | `#wrn-` |
| `important` | `#imp-` |
| `caution`   | `#cau-` |

## Blockquote

> qwert

> > > asfg

## LaTex

### 公式对齐

$$\begin{aligned}
  f(x) =& \sum_{k=0}^\infty \frac{1}{k!} x^k \\
  =& e^x
\end{aligned}$$

### 括号等高

$$\phi(x) = \frac{1}{\sqrt{2\pi}} \exp\left\{ \frac{1}{2} x^2 \right\} $$

### 矩阵

$$
\begin{bmatrix}
x_{11} & x_{12}&...&x_{1p} \\
x_{21} & x_{22}&...&x_{2p} \\
\vdots &\vdots &   &\vdots\\
x_{n1} & x_{n2}&...&x_{np} \\
\end{bmatrix}
$$

### 向量表示

$$   \boldsymbol{v} = (v_1, v_2)^T $$

## 定理类段落

术语

:   定义：三角形的内角和等于180°。

或者

引用[@thm-lebesgue01]。

::: {#thm-lebesgue01 name="勒贝格定理"}
一元函数黎曼可积， 当且仅当其不连续点的集合为零测集。
:::

| **环境名**  | **默认显示名** | **标签前缀** |
|-------------|----------------|--------------|
| theorem     | Theorem        | #thm-        |
| lemma       | Lemma          | #lem-        |
| corollary   | Corollary      | #cor-        |
| proposition | Proposition    | #prp-        |
| conjecture  | Conjecture     | #cnj-        |
| definition  | Definition     | #def-        |
| example     | Example        | #exm-        |
| exercise    | Exercise       | #exr-        |

## 代码块

### syntax highlight

```         
1 + 1
```

``` python
x = "abcde"
```

### raw content

```{=html}
<body>
    
<h>markdown_html</h>

<p></p> <abbr title="Mister"> Mr. </abbr>  </p>
<center>Center</center>

<dl>Description List

<dt>主题</dt>

<dd>描述</dd>

</dl>

<mark>Text highlight</mark>

<kbd>keyboard Ctrl+C</kbd>


<small>Text</small>
<body>
```
```{=latex}
\renewcommand*{\labelitemi}{\textgreater}
```
