---
subtitle: "quarto" 
date: "2024-10-08"
date-modified: last-modified
author: 
  name: "ANLIN"
  affiliation: "Independant 😀"
  email: anlinwang00@gmail.com
  roles: "made the document"
  
keywords: "dynamic report"
description: "<br/>good good study<br/>day day up"
title-block-banner: "#f0f3f5"
title-block-banner-color: "black"

code-fold: true
code-summary: "Show the code"
format: html
code-link: true
anchor-sections: true
link-external-icon: true
link-external-newwindow: true
theme:
  light: flatly
  dark: darkly # 深色模式
  
toc: true
number-sections: true
crossref: 
  fig-title: 图
  fig-prefix: 图
  tbl-title: 表
  tbl-prefix: 表
  eq-title: 式
  eq-prefix: 式
  def-title: 定义
  def-prefix: 定义
  lem-title: 引理
  lem-prefix: 引理
  sec-prefix: 章节
  
include-after-body: "footer.html"  # 页脚
css: style.css
include-in-header:  # caption 文本居中
   - text: |   
       <style>
       figcaption {
         text-align: center;
       }
       </style>

editor: visual
---

# 动态报告

<https://quarto.org/docs/guide/>

<https://www.productive-r-workflow.com/quarto-tricks>

## 文本格式 {#section-text_format}

+--------------------------------------------------------------------------+-----------------------------------------------------------+
| output                                                                   | syntax                                                    |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| `code`                                                                   | `` ` code ` ``                                            |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| **粗体**                                                                 | `**粗体**`                                                |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| *斜体*                                                                   | `*斜体*`                                                  |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| <mark>Text highlight</mark>                                              | `<mark>Text highlight</mark>`                             |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| [颜色标注]{style="color:red"}                                            | `[颜色标注]{style="color:red"}`                           |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| keyboard <kbd> Ctrl+C </kbd>                                             | `<kbd> Ctrl+C </kbd>`                                     |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| [下横线]{.underline}                                                     | `[下横线]{.underline}`                                    |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| ~~删除线~~                                                               | `~~删除线~~`                                              |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| 上标X^2^                                                                 | `X^2^`                                                    |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| 下标 X~1~                                                                | `X~1~`                                                    |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| 水平线分隔符                                                             | `***`                                                     |
|                                                                          |                                                           |
| ------------------------------------------------------------------------ |                                                           |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| <https://r4ds.hadley.nz/>                                                | `<https://r4ds.hadley.nz/>`                               |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| [quarto](https://quarto.org)                                             | `[quarto](https://quarto.org)`                            |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| {{< video https://www.youtube.com/embed/wo9vZccmqwc >}}                  | `{{< video https://www.youtube.com/embed/wo9vZccmqwc >}}` |
+--------------------------------------------------------------------------+-----------------------------------------------------------+
| > Blockquote                                                             | `> Blockquote`                                            |
+--------------------------------------------------------------------------+-----------------------------------------------------------+

## html

Here's some raw inline HTML: <a>html</a>

## YAML

### 添加页脚

您可以创建包含某些内容的文件。然后将其显示在 quarto 文档的底部。`html`

首先，创建一个名为 file 的文件。在其中复制以下内容：`footer.html`

在YAML block 中添加 `include-after-body: "footer.html"`

### 标题上方添加额外空间

使用自定义样式表可以直接实现此效果。此样式表将包含专门设计用于在标题上方添加额外空间的规则。

首先创建一个名为并包含以下规则的 CSS 文件：`style.css`

```         
h1, .h1, h2, .h2, h3, .h3 {
  margin-top: 84px;
}
```

这些 CSS 规则将在 1、2 和 3 级标题（分别由`h1` 、`h2` 和`h3` 标签表示）上方添加 84 像素的边距。

最后，在YAML block 中添加 `css: style.css`

## 内部链接

如 [文本格式](#section-text_format) 是第一节

## 脚注

第一个[^1]

[^1]: WANG,A.,et al.(2025)

For instance[^2], here is one attached to the word carrot[^3].

[^2]: dafhaifhafoahfo

[^3]: The carrot (Daucus carota subsp. sativus) is a root vegetable, typically orange in color

### Execute chunk

+-----------+---------+----------------------------------------------------------+
| Option    | Default | Effects                                                  |
+===========+=========+==========================================================+
| `echo`    | `true`  | `false`: hide code in output\\                           |
|           |         |                                                          |
|           |         | :   include code cell syntax`fenced`                     |
+-----------+---------+----------------------------------------------------------+
| `eval`    | `true`  | `false`: don’t run code                                  |
+-----------+---------+----------------------------------------------------------+
| `include` | `true`  | `false`: don’t include code or results                   |
+-----------+---------+----------------------------------------------------------+
| `output`  | `true`  | `false`: don’t include results\\                         |
|           |         |                                                          |
|           |         | :   treat results as raw markdown`asis`                  |
+-----------+---------+----------------------------------------------------------+
| `warning` | `true`  | `false`: don’t include warnings in output                |
+-----------+---------+----------------------------------------------------------+
| `error`   | `false` | `true`: include error in output and continue with render |
+-----------+---------+----------------------------------------------------------+

## Figure

### Caption

```{r}
#| fig-align: center
#| fig-width: 6
#| fig-height: 6
#| fig-cap: 箱线图
#| fig-cap-location: top
library(tidyverse)

mpg %>%
  ggplot(aes(x = reorder(class, hwy), y = hwy, fill = class)) +
  geom_boxplot() +
  xlab("class") +
  theme(legend.position = "none")
```

标题文本居中

```         
include-in-header:
   - text: |
       <style>
       figcaption {
         text-align: center;
       }
       </style>
```

```{r}
#| label: fig-plot
#| fig-cap: 组图
#| fig-subcap:
#|   - "点"
#|   - "线"
#| layout-ncol: 2
#| column: page-right

plot(1:25,1:25,pch=c(1:25))
plot(1:25,1:25,type="o",pch=c(1:25))
```

## Pandoc Div块

Div .class `.panel-tabset .nav-pills`

::: {.panel-tabset .nav-pills}
### Scatterplot

```{r, warning=FALSE}
mpg %>%
  ggplot(aes(x = reorder(class, hwy), y = hwy, fill = class)) +
  geom_point() +
  xlab("class") +
  theme(legend.position = "none")

```

### Boxplot

```{r, warning=FALSE}
mpg %>%
  ggplot(aes(x = reorder(class, hwy), y = hwy, fill = class)) +
  geom_boxplot() +
  xlab("class") +
  theme(legend.position = "none")
```

### Barplot

```{r, warning=FALSE}
mpg %>%
  ggplot(aes(x = reorder(class, hwy), y = hwy, fill = class)) +
  geom_bar(stat = "identity") +
  xlab("class") +
  theme(legend.position = "none")
```
:::

如左图 @fig-plot-1 所示，点有25种不同的形状，

右图 @fig-plot-2 所示。

```{r}
#| label: fig-输出复杂排版图片
#| fig-cap: 复杂排版组图输出
#| fig-subcap:
#|   - 汽车
#|   - 压力
#|   - mtcars
#| layout: [[1], [1, 1]]

plot(cars)
plot(pressure)
plot(mtcars)
```

## 表格

@tbl-stats displays basic summary statistics for these two variables.

```{r}
#| label: tbl-stats
#| tbl-cap: "Table Summary statistics "

mpg %>%
  summarise(
    mean_displ=mean(displ),
    mean_hwy=mean(hwy),
    mean_cty=mean(cty),
    .by = cyl
    ) %>%
  knitr::kable(digits = c(0, 0, 0, 0, 2))
```

## 公式 {#sec-formula}

Black-Scholes (@eq-black-scholes) is a mathematical model that seeks to explain the behavior of financial derivatives, most commonly options:

$$ \frac{\partial \mathrm C}{ \partial \mathrm t } + \frac{1}{2}\sigma^{2} \mathrm S^{2} \frac{\partial^{2} \mathrm C}{\partial \mathrm C^2}   + \mathrm r \mathrm S \frac{\partial \mathrm C}{\partial \mathrm S}\ =   \mathrm r \mathrm C  $$ {#eq-black-scholes}

We can fit a simple linear regression model of the form shown in @eq-slr.

$$
price = \hat{\beta}_0 + \hat{\beta}_1 \times area + \epsilon
$$ {#eq-slr}

## Callout

::: callout-note
Note that there are five types of callouts, including: `note`, `tip`, `warning`, `caution`, and `important`.
:::

::: callout-tip
This is an example of an tip callout
:::

::: callout-caution
This is an example of an caution callout
:::

::: callout-warning
This is an example of an warning callout
:::

::: callout-important
This is an example of an important callout
:::

::: {#tip-example .callout-tip}
交叉引用 a Tip

Add an ID starting with `#tip-` to reference a tip.
:::

See @tip-example...

自定义callout

:::: callout-gradient
::: callout-note
This is a custom callout.

Using CSS, you can control pretty much everything.

This div is even shaking every now and then 🙃
:::
::::

| 标注类型    | 前缀    |
|-------------|---------|
| `note`      | `#nte-` |
| `tip`       | `#tip-` |
| `warning`   | `#wrn-` |
| `important` | `#imp-` |
| `caution`   | `#cau-` |

## 页边距

### R结果

```{r}
#| column: margin

knitr::kable(
  mtcars[1:3, 1:3]
)
```

### Div

::: column-margin
Hi! I'm a side note! 🔥
:::

## LaTex

### 公式对齐

$$\begin{aligned}
  f(x) =& \sum_{k=0}^\infty \frac{1}{k!} x^k \\
  =& e^x
\end{aligned}$$

### 括号等高

$$\phi(x) = \frac{1}{\sqrt{2\pi}} \exp\left\{ \frac{1}{2} x^2 \right\} $$

### 矩阵

$$
\begin{bmatrix}
x_{11} & x_{12}&...&x_{1p} \\
x_{21} & x_{22}&...&x_{2p} \\
\vdots &\vdots &   &\vdots\\
x_{n1} & x_{n2}&...&x_{np} \\
\end{bmatrix}
$$

### 向量表示

$$   \boldsymbol{v} = (v_1, v_2)^T $$

## 定理类段落

术语

:   定义：三角形的内角和等于180°。

或者

引用[@thm-lebesgue01]。

::: {#thm-lebesgue01 name="勒贝格定理"}
一元函数黎曼可积， 当且仅当其不连续点的集合为零测集。
:::

| **环境名**  | **默认显示名** | **标签前缀** |
|-------------|----------------|--------------|
| theorem     | Theorem        | #thm-        |
| lemma       | Lemma          | #lem-        |
| corollary   | Corollary      | #cor-        |
| proposition | Proposition    | #prp-        |
| conjecture  | Conjecture     | #cnj-        |
| definition  | Definition     | #def-        |
| example     | Example        | #exm-        |
| exercise    | Exercise       | #exr-        |

## \_opts_chunk\$set.R

```{r}
knitr::opts_chunk$set(
  # comment = "#>",
  # collapse = TRUE,
  # cache = TRUE,
  # message = FALSE,
  # error = FALSE,
)
ggplot2::theme_set(new = ggplot2::theme_classic())
```

## 内联代码

Use computed values directly in text sections. Code is evaluated at render and results appear as text.

```{r}
#| code-fold: show
a <- 1+2+3
```

#### Knitr

a 的值为 `` `r a` ``

## 会话信息

<button class="accordion-button" type="button" data-bs-toggle="collapse" data-bs-target="#collapseOne">

<mark><b><i>Session Information,click to show</i></b></mark>

</button>

::: {#collapseOne .accordion-collapse .collapse style="color: red"}
```{r}
sessionInfo()
```
:::
